---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  message = F,
  warning = F
)
```

# `repdemoproj` 

<!-- badges: start -->
<!-- badges: end -->

The goal of `repdemoproj` is to demonstrate a reproducible data analysis project.

## Docker

Run this project in Docker.
```
docker pull xmjandrews/verse:20.06.25
docker run --rm -p 8787:8787 -e PASSWORD=<passwd> -e ROOT=true -v <local drive>:/home/rstudio xmjandrews/verse:20.06.25
```

The `Dockerfile` for the Docker image is also available [here](Dockerfile).


## Package

```{r, echo=F, results='hide'}
# If it's installed, uninstall it.
if ('bayeslmm' %in% rownames(installed.packages())){
  devtools::uninstall('bayeslmm')
}
```


Install the package from the local `bayeslmm` directory like this (where `upgrade = F` means that it does not ask you to update dependencies):
```{r, results='hide'}
devtools::install_local('bayeslmm', upgrade = F)
```
```{r, echo=F, results='hide'}
# uninstall it so that we can re-install it from GitHub next
devtools::uninstall('bayeslmm')
```

Or install it from GitHub like this:
```{r, eval=T, results = 'hide'}
devtools::install_github("https://github.com/mark-andrews/repdemoproj.git", 
                         subdir = 'bayeslmm', 
                         upgrade = F)
```

Then, load it and use it like this.

```{r demo, eval=T, results='hide'}
library(bayeslmm)
lmmplot(sleepstudy_df)
```


