---
title: "A Bayesian Mixed Effects Linear Model"
author: "Mark Andrews"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

```{r}
# Load the `bayeslmm` package
library(bayeslmm)

# Load `here` for handling relative paths
library(here)
```


# Introduction

We will analyse a sleep deprivation data using a Bayesian linear mixed effects model.
The data is displayed in Figure \ref{fig:sleepdeprivplot}.
The linear mixed effects model is based on
$$
y_i \sim N(\mu_i, \sigma^2),\quad \mu_i = \beta_{[0,s_i]} + \beta_{[1,s_i]} x_i,
$$
where $y_i$ is the reaction time on observation $i$, $x_i$ is the number of days without sleep, $s_i \in \{1, 2 \ldots J\}$  the identity of the subject on observation $i$.

```{r sleepdeprivplot, fig.cap="Reaction time as a function of sleep deprivation. Each subplot shows a different participant in the sleep deprivation study.", fig.align="center", out.width="0.67\\textwidth"}
lmmplot(sleepstudy_df)
```

```{r}
results_0 <- readRDS(here('tmp/model_0.rds'))
results_1 <- readRDS(here('tmp/model_1.rds'))
```

The estimates of the fixed effects of a varying intercept model are shown in the following table.
```{r}
knitr::kable(brms::fixef(results_0$model),
             format = 'latex',
             digits = 2,
             booktabs = TRUE) %>% 
  kableExtra::kable_styling(position = 'center')
```

